\section{Introduction}\label{sec:intro}



%\input{sections/ccf22-problem-description}
\input{ccf23-problem-description}
\input{ccf23-research-objectives}


%\subsection{Significance of This Proposed Project: NSF Merit Criteria}

\section{Intellectual Merits}

This project will advance the state-of-the-art
knowledge and scientific foundations in AI/ML for Code.
%They are transformative and directly help improve
%software engineering tools empowered by AI/ML by breaking down
%barriers and making the world of coding accessible to all, regardless
%of visual impairments, contributing to a more diverse and vibrant
%programming community.

\noindent \underline{{\bf Advance the state-of-the-art knowledge and
    understanding}}. Voice-driven programming framework will advance
the body of knowledge and theoretical foundations for machine learning
and AI for code. The empirical study in Thrust 1 will help advance the
state-of-the-knowledge on assistive technology for VIPLs.

\noindent \underline{{\bf Scientific foundation, creative/original
    research}}. This project will provide a scientific foundation
(novel concepts, representations, algorithms, models, and tools) (1)
to enable voice-driven assistive technology, (2) to advance the AI/ML
models in both voice recognition and code generation, and (3) to
enable the applications of AI/ML for code research in building
interactive IDEs for VIPLs.

\section{Broader Impacts}

\underline{{\bf (1) Transformative and benefits to society}}.  Our
novel IDE equips individuals with visual
impairments with a versatile set of tools,
enabling an interactive programming experience while reducing
accessibility obstacles. Our goal is to eliminate these barriers and
ensure that the programming world is open to everyone, irrespective of
visual impairments, thereby enhancing the diversity and vitality of
programming.


\noindent\underline{{\bf (2) Foster other related research
    activities}}. We will produce theoretical concepts and techniques
that are novel in Machine Learning, e.g., novel neural networks for
code (AI4Code), as well as {\em human-computer interaction} (HCI) and
behavioral science, especially toward visually-impaired
programmers. Our results will foster {\em research in related fields
  of {\em machine learning} (ML) and {\em software engineering} (SE)}.

%The applications of our neural program analysis in software
%engineering applications will advance software security and
%reliability.

\noindent\underline{{\bf (3) Education, dissemination, and broader
    participation}} ({\em Section~\ref{edu}}). The research will enhance the
infrastructure for teaching/research via tools and data sets for use
by students and practitioners, and for enhancement by researchers. We
will provide related learning modules for educators as well. It will
include outreach activities for undergraduate students,
underrepresented groups, minorities, and women in science.
