\section{Introduction}
\label{sec:intro}

\input{ccf24-problem-description-2.tex}

\input{ccf24-research-objectives}


%\subsection{Significance of This Proposed Project: NSF Merit Criteria}

%\section{Relevance to Secure and Trustworthy Cyberspace}

%This project will develop novel concepts, representations, algorithms,
%models, and tools to support early software vulnerability
%detection. It is transformative and directly help improve software
%quality with novel program analysis-based software security and
%vulnerability detection tools on code snippets.

\section{Intellectual Merits}

%The results of this project will be transformative and directly help
%improve software quality with novel program analysis-based software
%security tools.

\noindent \underline{{\bf Advance the state-of-the-art knowledge and
    understanding}}. Predictive program analysis infrastructure in Thrusts
1--3 will advance the body of knowledge and theoretical foundations
in the area of {\bf machine learning and AI for code}. Thrust 4 will also help advance the practical tools in software engineering.

\noindent \underline{{\bf Scientific foundation, creative/original
    research}}. (1) to enable the analysis on partial code, (2) to empower
the program analysis techniques on both (in)complete code,
and (3) to enable the applications of program analysis on incomplete
code such as runtime error and vulnerability detection for code snippets, debugging tools for code under editing, etc.

\section{Broader Impacts}

\underline{{\bf (1) Transformative and benefits to society}}. Our
results will be transformative and directly benefit to our society.
They will lead to increasing developers' productivity, software
quality \& reliability.  Our validation involves students and
professionals, promoting teaching, training, and learning of both {\bf
  program analysis} and {\bf machine learning} techniques that
have wide impacts in industry and academic communities.

\noindent\underline{{\bf (2) Foster other related research
    activities}}. Our results will foster {\em research activities in
  related fields of {\bf machine learning} and {\bf software security}},
and the applications in software security and reliability.
%We will produce theoretical concepts and techniques that are novel in
%deep learning, e.g., novel neural networks to model and learn for
%code.
%The applications of our neural program analysis in software
%engineering applications will advance software security and
%reliability.

%The collected {\bf large scale bug\&fix corpus} will be useful for
%software quality and reliability research.
%Innovations in CRL could be used to {\bf advance other SE tasks}. We
%will also develop {\bf novel DL-based bug detect-fix} approaches.


\noindent\underline{{\bf (3) Education, dissemination, and broader participation}} (Section~\ref{edu}). The
research will enhance the infrastructure for teaching/research via
tools and data sets for use by students and practitioners, and for
enhancement by researchers. We will provide related learning
modules for educators as well. It will include outreach activities for
undergraduate students, underrepresented groups, minorities, and women
in science.
%contribute novel
%teaching modules to our curriculum.
%Details will be presented in Section~\ref{edu}


\iffalse
\begin{itemize}
	\vspace{-5pt}
\itemsep-0.2em 
  \item {\bf Transformative and benefits to society}. Our 
    results will be transformative and directly benefit to our
    society. 
    They will lead to increasing developers' productivity
    and software quality \& reliability. 
    Our validation involves students and
    professionals, promoting teaching, training, and learning of bug detecting and fixing techniques that have wide impacts 
    in industry and academic communities.

%report

  \item {\bf Foster other research activities}. Our results will
    foster research activities in related fields of deep learning and
    software quality. 
    This project will produce theoretical
    concepts and techniques that are novel even in deep learning, e.g.,
    novel neural networks for modeling and learning code. 
    The collected large scale bug fixing corpus will be useful for software quality and reliability research in general.
    %e.g.,   code transformation. 
%    This project will also advance
%    the state-of-the-art research in large-scale program analysis with
%    deep neural network models.

%The representation for software security vulnerabili will be useful in
%research on software security, malware detection, vulnerability
%reports, and automatic security patching.


  \item {\bf Education, dissemination, and broader participation}.
  The research will enhance the infrastructure for teaching and
  research by providing tools and data sets for use by students and
  practitioners, and for enhancement by other researchers. We will
  provide related learning modules for educators as well. It will
  contribute novel teaching modules to our curriculum. Details will be
  presented in Section~\ref{edu}

%Details are in Section 4.

\end{itemize}
\fi
