\section{Dissemination and Educational Plan}
\label{edu}

\paragraph{Engaging Students into Research}

This project will create opportunities for students at UT-Dallas to
participate into cutting-edge research: PI Nguyen has currently supported
four female students (2 PhD students and 2 undergraduates), with a total
of four PhD students, two M.Sc. students, and four undergraduates.

%has worked with 6 undergraduate students (i.e., two are female
%students) and two master students (i.e., independent
%study). Additionally, PI Wang is actively doing research with a group
%of two undergraduate students (Vrushali Koli (female) from NJIT and
%Delmond Wyllis from Rowan Univ. in NJ) and \underline{six high-school
%students} in the NJ Governor's STEM Scholars Program.  PI Wang
%supervise 4 Ph.D students (one female) and 1 master student.


%(2) {\em UTD's Collegium Honors Program}:
%{\em ISU's Freshman Honor program}: 
%PI Nguyen has been engaging two freshman honor students into his
%research program since he joined UTD in 2016. 
%REU supplements will be requested to support this undergraduate research; 
%
%(3) {\em HackersUTD}: This Fall, UT Dallas Computer Science department
%welcomed 2,876 students, including 466 CS/software engineering
%freshmen, with activities and events as a way to welcome and
%familiarize students with the UT Dallas CS. We will engage members of
%this organization; 
%(3) UT Dallas works with North Texas high school
%seniors to host IT empowerment for their camps. To generate interests
%in computing studies from {\em high-school} students in Dallas area,
%we will involve them in design projects that target the use of
%software in teaching {\em K-12} subjects; 
%(2) {\em UTD's Women Who
%Compute}: The PI Nguyen has actively used this program to generate interests
%in SE research from women students. From the past, PI Nguyen has
%mentored 3 women students; 
%(Dong Fei, Kristina Gervais, Taylor Schreck); 
%(3) {\em Involving Under-represented Minorities}: We
%will attract minority students funded by GEM fellowships, involve
%high-school teachers via Alliances for Graduate Education and the
%Professoriate.
%and UT Dallas Programs for Minors: we will work
%with this program to recruit more student in minority.

%This project will also create opportunities for students at UT-Dallas:
PI Nguyen has extensive experience in engaging students in outreach
programs: (1) {\em Collaborative educational project between UT-Dallas
and Fulbright University Vietnam (FUV)}: Through this program, PI
Nguyen has been mentoring a honor thesis project for two undergraduate
students that has been conducting the preliminary empirical study
described in Section~\ref{sec:thrust1}. PI Nguyen is also a mentor for
two visually-impaired students at FUV, Tran Viet Hoang and Tran Trong
Nghia, who have been extremely helpful for our preliminary study.
(2) {\em UTD's Collegium Honors Program}: He
has been engaging several freshman honor students into his research
program since 2005. (3) {\em HackersUTD}: In Fall'19, UT Dallas CS
welcomed 2,876 students, including 466 freshmen, with activities and
events as a way to familiarize students with CS/SE. We will use the
results of this project in this program.
%
(4) UT Dallas works with {\em North Texas high school seniors to host
IT empowerment} for their camps. To generate interests in computing
studies from {\em high-school} students in Dallas area, PI Nguyen has
been involving them in design projects that target the use of software
in teaching {\em K-12} subjects; (5) {\em UTD's Women Who Compute}: he
has actively used this program to generate interests in SE research
from women students. PI Nguyen has mentored several {\em female
undergraduate students} (Weining Gao, Kristina Gervais, Taylor
Schreck, etc.); Currently, he supervise two undergraduate students
(Dao Ngoc, Nam Anh) and two female PhD students (Mary Grace Kozuch and
Hridya Dhulipala) (6) {\em Involving Under-represented Minorities}: We
will attract minority students funded by GEM fellowships, involve
high-school teachers via Alliances for Graduate Education and the
Professoriate; and (7) {\em UT Dallas Programs for Minors}: we will
work with this program to recruit more student in minority.


\paragraph{Dissemination of Research and Teaching Materials}

Beside publications at professional \emph{conferences, journals} and
public Web sites, we will explore:
%$use the available resources at UT-Dallas
%through various forums for dissemination.
%
%PI Wang is a member of DIMACS~\cite{dimacs}, the Center for Discrete
%Mathematics and Theoretical Computer Science as an NSF-funded Science
%and Technology Center (STC) and a New Jersey Commission on Science and
%Technology Advanced Technology Center. DIMACS has over 350 members
%across the U.S. PI Wang will continue to advocate our research through
%DIMACS events, research and academic programs.  PI Wang will use
%the \textit{annual NJIT Research Showcase and President Forum} to show
%our accomplishments to all NJIT people.
%PI Nguyen will continue to use the following resources:
(1) TExAs Software Engineering Research (TEASER) Doctoral Symposium:
where SE researchers from the DFW Metroplex (and beyond) meet to
discuss and work on SE topics.  The mission of TEASER is to provide a
supportive space in which PhD students can present and receive
feedback on their research work, while at the same time giving both
researchers and students a venue to get to know one another and
network productively.  (2) American Society for Engineering Education:
PI Nguyen, with his prior NSF-funded TUES project, has disseminated
educational results via this channel.
%He will continue to disseminate educational outcomes via this
%educational society.
(3) Leadership through Engineering Academic Diversity (LEAD): PI
Nguyen have served as mentors for this program which aims to enrich
educational experience of {\em minority engineering students}.

%\paragraph{Research Community Building.}

%PI Nguyen has successfully organized the 1st {\bf International
%Workshop on Representation Learning for Software Engineering and
%Programming Languages (RL+SE\&PL 2020)}~\cite{rlsepl}, associated with
%ESEC/FSE'20. The workshop had 104 paid registers and featured one
%keynote speaker (Dr. Miltos Allamanis, well-known CRL scientist at
%Microsoft Research) and six technical presentations. RL+SE\&PL'20 has
%sparked constructive and inspiring discussions. With its success, we
%are building a diverse and active community. We plan to build on the
%success of the first edition to continue this series to disseminate
%ideas to a wider community, and to build a larger community bridging
%SE and ML.
