\section{Introduction}\label{sec:intro}



%\input{sections/ccf22-problem-description}
\input{satc22-problem-description}
\input{satc22-research-objectives}


%\subsection{Significance of This Proposed Project: NSF Merit Criteria}

\section{Relevance to Secure and Trustworthy Cyberspace}

\subsection{Intellectual Merits}

The results of this project will advance the state-of-the-art
knowledge and scientific foundations in both software security and
machine learning (explainable AI). They are transformative and
directly help improve software quality with novel automated software
vulnerability detection and assessment techniques.

\noindent \underline{{\bf Advance the state-of-the-art knowledge and
    understanding}}. Explainable AI-enabled vulnerability detection in
both binary and source code in Thrusts 1 and 3 will advance the body
of knowledge and theoretical foundations for both areas of machine
learning for code and software security. Thrust 2 will also help
advance the practical tools in software security and engineering.

\noindent \underline{{\bf Scientific foundation, creative/original
    research}}. This project will provide a scientific foundation
(novel concepts, representations, algorithms, models, and tools) (1)
to enable the explanations for ML models in vulnerability detection,
(2) to empower the ML-based vulnerability detection and assessment.

%and (3) to enable the applications of program analysis on incomplete
%code such as vulnerability detection on code snippets, code
%completion, etc.

\subsection{Broader Impacts}

\underline{{\bf (1) Transformative and benefits to society}}. Our
results will be transformative and directly benefit to our society.
They will lead to increasing software quality \& reliability, software
security.  Our validation involves students and professionals,
promoting teaching, training, and learning of both {\bf software
  security} and {\bf machine learning} techniques that have wide
impacts in industry and academic communities.

\noindent\underline{{\bf (2) Foster other related research
    activities}}. Our results will foster {\em research activities in
  related fields of {\bf explainable AI/ML} and {\bf software
    engineering}}. We will produce theoretical concepts and techniques
that are novel in deep learning, e.g., XAI model for source and binary
code. The applications of our techniques in software engineering
applications will advance software security and reliability.

%The collected {\bf large scale bug\&fix corpus} will be useful for
%software quality and reliability research.
%Innovations in CRL could be used to {\bf advance other SE tasks}. We
%will also develop {\bf novel DL-based bug detect-fix} approaches.


\noindent\underline{{\bf (3) Education, dissemination, and broader participation}} (Section~\ref{edu}). The
research will enhance the infrastructure for teaching/research via
tools and data sets for use by students and practitioners, and for
enhancement by researchers. We will provide related learning
modules for educators as well. It will include outreach activities for
undergraduate students, underrepresented groups, minorities, and women
in science.
%contribute novel
%teaching modules to our curriculum.
%Details will be presented in Section~\ref{edu}



