%% Should originally belong to \subsection{Working Demo}.
%% Moving it here to move the image up a page.
\input{icse23-demo-sections/screenshot2.tex}

\section{Getting Started with \tool}
\subsection{Environment Setup}
\tool was implemented as a Python package using 
several libraries including \code{pytorch}, \code{transformers}, \code{pyvis},
etc. A working environment can be set up with the help of 
\code{conda} package manager in the Anaconda Python distribution~\cite{anaconda}, 
and the provided YAML configuration file with the following 
command: \code{\$ conda env create -f environment.yml}

\subsection{Usage}
The prototype for \tool can be run in the virtual environment as a command-line utility as follows:

\noindent \code{\$ python infer.py -i <input-path> -o <output-format>}
\begin{itemize}
    \item \code{-i}: Path to a \code{.txt} file containing the code snippet, or a directory containing multiple input \code{.txt} files. 
    \item \code{-o \{json|html\}}: \code{json} option outputs a JSON file containing predicted CFG/PDG edge information between the statements in the code snippet(s). \code{html} option draws an interactive directed graph bearing CFG (\textit{blue}) and PDG (\textit{red}) edges, further saving it as an HTML file(s). 
\end{itemize}

After loading the pre-trained dependency inference model, \tool takes a blazing quick 
%\textcolor{red}{0.\_\_} seconds on an Intel 8\textsuperscript{th} generation CPU and is even faster on a machine with a GPU ($\sim$0.02 seconds with an Nvidia Quadro P4000 GPU).
$\sim$0.02 seconds on a machine with an Nvidia Quadro P4000 GPU.

\subsection{Working Demo}
In Figure~\ref{fig:demo}, we illustrate a working demonstration of \tool. At the top, we present two Java code snippets: partial (left), and complete (right). The corresponding CFG/PDGs drawn by \tool are drawn at the bottom. The control-flow edges and program dependence edges are highlighted in \textit{blue} and \textit{red} colors respectively. Clicking on a node bolds all edges coming to, or leaving the node. In addition, hovering over a node lists the corresponding statement in a text box.

In the partial code snippet (left), statement-block $S_3$--$S_4$ iterates over the variable \code{allGames} defined in statement $S_1$. Due to the loop dependence, program (data)-dependence edges $S_1{\rightarrow}S_3$ and $S_1{\rightarrow}S_4$ are identified (left-bottom). Besides, a \textit{def-use} chain and consequently, a data-dependence edge $S_1{\rightarrow}S_6$  over the identifier \code{allGames} is also identified.

For the complete code snippet (right), all control-flow edges are predicted accurately. In addition, \tool predicts all but one control-dependence edge, that from $S_2{\rightarrow}S_7$. However, given that it correctly identifies the control-flow edge between $S_2$ and $S_7$, it is likely that it was not able to conclude whether $S_2$ determines the execution of $S_7$, resulting in the miss.

Statements such as "\code{\{}" or "\code{\}}" are not syntactic statements, and do not share a dependence relation with other statements in the code snippet. Thus, our tool draws them as free nodes $S_5$ (left-bottom); $S_6$, $S_7$, and $S_9$ (right-bottom) in the graphs.

\subsection{Tool Availability}
All code and data used to build and run \tool is available at {https://github.com/deeppda-icse23/DeepPDA}. Also, our video demo can be found at \textcolor{red}{{Add.Youtube.video.link}}.